---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

please ignore this change

# loquiAPI

<!-- badges: start -->
<!-- badges: end -->

The goal of loquiAPI is to empower users to programmatically generate automated videos from Google Slides or Microsoft PowerPoint slides. By utilizing the API hosted on Fred Hutch's servers, accessible at <https://loquiapi.fredhutch.org/__docs__/> and using R functions like `generate_from_gs()`, users gain the ability to produce numerous videos simultaneously from various sets of slides in Google Slides or PowerPoint.

## Installation

You can install the development version of loquiAPI from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FredHutch/loquiAPI")
```

## Example

When you want to generate a video of your Google Slides, run `generate_from_gs(link)` and you should see the output file path to your video mp4 file.

```{r, eval = FALSE}
library(loquiAPI)

generate_from_gs(link = "https://docs.google.com/presentation/d/1Dw_rBb1hySN_76xh9-x5J2dWF_das9BAUjQigf2fN-E/edit#slide=id.p")
```

## More Voice Options

If you'd like to explore different voices but aren't certain about the available options, you can visit the [CoquiTTS](https://huggingface.co/spaces/coqui/CoquiTTS) Hugging Face Space. Once you find a voice you like, please let me know by submitting a GitHub issue and I will make sure to include it.
